Classical density functional theory for the square-well liquid

### 2014-07-23 papers/square-well-liquid/paper.tex
Added Fourier transforms of radial distribution polynomial expansion for square well liquid. Tested on knightley. Took 0:25.41.

For or purposes, we want to Fourier transform $g_s(r,g_\sigma)u_{SW}(\rr)$ and
the square well potential since it is used in the free energy functional.
\begin{align}
  \tilde{g_s}(k, g_\sigma) =\int^\infty_{-\infty} g_s(r, g_\sigma)u_{SW}(\rr)e^{-i\kk \cdot \rr}\mathrm{d}^3\rr
\end{align}
Since the radial distribution function and potential are radially symmetric, we can
express the dot product differently so that the transform is
\begin{align}
  \tilde{g_s}(k, g_\sigma) &=\int^\infty_{-\infty} g_s(r,
  g_\sigma)u_{sw}(r)e^{-ikr \cos \theta}\mathrm{d}^3\rr \\
  &= 2 \pi \int_\sigma^{\lambda \sigma} \int_0^\pi g_s(r, g_\sigma) e^{-ikr \cos
    \theta} r^2 \sin \theta \, \mathrm{d}r \mathrm{d}\theta \\
  &= 2\pi\int_\sigma^{\lambda \sigma} \int_{1}^{-1} g_s(r, g_\sigma) e^{-ikr \cos
    \theta} r^2 \mathrm{d}r \mathrm{d}\cos \theta \\
  &= 2\pi\int_\sigma^{\lambda \sigma} g_s(r, g_\sigma) \frac{1}{-ikr}\bigg[e^{ikr} -
    e^{-ikr} \bigg]r^2 \mathrm{d}r \\
 &= \frac {4\pi}{k}\int_\sigma^{\lambda \sigma} r g_s(r,g_\sigma) \sin (kr) \mathrm{d}r.
\end{align}
Now I'll do the separate integrals for each part on the right hand
side of Eqn. \ref{eq:gs}. The first term is 1, so we are left with
a delta function.  We will ignore this term, and
move onto the next one whose integral is
\begin{align}
  \int_\sigma^{\lambda \sigma}r(g_\sigma -1) e^{-\kappa_0
    \left( \frac{r}{\sigma}-1 \right)} \sin(kr)\mathrm{d}r.
\end{align}
If we pull out constants and put this into Mathematica,
\begin{widetext}
  \begin{align}
  \int_\sigma^{\lambda
    \sigma}re^{-\frac{\kappa_0}{\sigma}r}\sin(kr)\mathrm{d}r
  &= \frac{1}{(k^2 + (\kapovsig{0})^2)^2} \bigg\{ e^{-\kappaO} \left[k
      \left(2\kapovsig{0} + \sigma (k^2 + (\kapovsig{0})^2) \right)
      \cos (\sigma k) + \left((\kapovsig{0})^2(1 + \kappaO) +
      k^2(\kappaO-1)\right) \sin (\sigma k) \right] \notag \\
  &- e^{-\lambda
    \kappaO} \left[ k
      \left(2\kapovsig{0} + \lambda \sigma (k^2 + (\kapovsig{0})^2) \right)
      \cos (\lambda \sigma k) + \left((\kapovsig{0})^2(1 + \lambda \kappaO) +
      k^2(\lambda\kappaO-1)\right) \sin (\lambda \sigma k)\right] \bigg\}
  \end{align}
\end{widetext}
\subsubsection{Averaged pair distribution  $g_\sigma(\rr)$}

>>>>

For or purposes, we want to Fourier transform $g_s(r,g_\sigma)u_{SW}(\rr)$ and
the square well potential since it is used in the free energy functional.
\begin{align}
  \tilde{g_s}(k, g_\sigma) =\int^\infty_{-\infty} g_s(r, g_\sigma)u_{SW}(\rr)e^{-i\kk \cdot \rr}\mathrm{d}^3\rr
\end{align}
Since the radial distribution function and potential are radially symmetric, we can
express the dot product differently so that the transform is
\begin{align}
  \tilde{g_s}(k, g_\sigma) &=\int^\infty_{-\infty} g_s(r,
  g_\sigma)u_{sw}(r)e^{-ikr \cos \theta}\mathrm{d}^3\rr \\
  &= 2 \pi \int_\sigma^{\lambda \sigma} \int_0^\pi g_s(r, g_\sigma) e^{-ikr \cos
    \theta} r^2 \sin \theta \, \mathrm{d}r \mathrm{d}\theta \\
  &= 2\pi\int_\sigma^{\lambda \sigma} \int_{1}^{-1} g_s(r, g_\sigma) e^{-ikr \cos
    \theta} r^2 \mathrm{d}r \mathrm{d}\cos \theta \\
  &= 2\pi\int_\sigma^{\lambda \sigma} g_s(r, g_\sigma) \frac{1}{-ikr}\bigg[e^{ikr} -
    e^{-ikr} \bigg]r^2 \mathrm{d}r \\
 &= \frac {4\pi}{k}\int_\sigma^{\lambda \sigma} r g_s(r,g_\sigma) \sin (kr) \mathrm{d}r.
\end{align}
Now I'll do the separate integrals for each part on the right hand
side of Eqn. \ref{eq:gs}. The first term is 1, so we are left with
a delta function.  We will ignore this term, and
move onto the next one whose integral is
\begin{align}
  \int_\sigma^{\lambda \sigma}r(g_\sigma -1) e^{-\kappa_0
    \left( \frac{r}{\sigma}-1 \right)} \sin(kr)\mathrm{d}r.
\end{align}
If we pull out constants and put this into Mathematica,
\begin{widetext}
  \begin{align}
  \int_\sigma^{\lambda
    \sigma}re^{-\frac{\kappa_0}{\sigma}r}\sin(kr)\mathrm{d}r
  &= \frac{1}{(k^2 + (\kapovsig{0})^2)^2} \bigg\{ e^{-\kappaO} \left[k
      \left(2\kapovsig{0} + \sigma (k^2 + (\kapovsig{0})^2) \right)
      \cos (\sigma k) + \left((\kapovsig{0})^2(1 + \kappaO) +
      k^2(\kappaO-1)\right) \sin (\sigma k) \right] \notag \\
  &- e^{-\lambda
    \kappaO} \left[ k
      \left(2\kapovsig{0} + \lambda \sigma (k^2 + (\kapovsig{0})^2) \right)
      \cos (\lambda \sigma k) + \left((\kapovsig{0})^2(1 + \lambda \kappaO) +
      k^2(\lambda\kappaO-1)\right) \sin (\lambda \sigma k)\right] \bigg\}
  \end{align}
\end{widetext}
\subsection{Polynomial expansion}

A different way to do this that avoids some of the Fourier transform
troubles is to formulate $g_S$ as a polynomial expansion.  We do this
up to fouth order so that
\begin{align}
  g_S(r;g_\sigma) &=
  g_\sigma + \sum_{i=1}^{4} \sum_{j=1}^{4} \kappa_{ij} (g_\sigma - 1)^i
  \left(\frac{r}{\sigma}-1\right)^j,
  \label{eq:fit-form}
\end{align}
which makes the transforms for $i=1,2,3,4$
\begin{align}
 \frac {4\pi}{k}\int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^i \sin (kr) \mathrm{d}r.
\end{align}
Let's do a u-substitution where $u= \frac{r}{\sigma}-1$, then the
integral becomes
\begin{align}
 \frac {4\pi}{k}\int_0^{\lambda -1} \sigma^2 (u+1)u^i \sin(k\sigma
       [u+1]) \mathrm{d}u.
\end{align}
Now we calculate the integrals.
\begin{widetext}
\begin{align}
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right) \sin (kr) \mathrm{d}r =&
 \frac{1}{k^3 \sigma}\left[(2-\lambda k^2
 \sigma^2(\lambda-1))\cos(k\lambda\sigma)-k\sigma(\sin(k\sigma)
 +(1-2\lambda) \sin(k\lambda\sigma)) -\cos(k\sigma) \right] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^2 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^4\sigma^2} \big[
 6\sin(k\sigma)+(k^2\sigma^2(1-4\lambda+3\lambda^2)
 -6)\sin(k\lambda\sigma) \notag \\
 &-2k\sigma\cos(k\sigma) - k\sigma(4 +
 \lambda(k^2\sigma^2(\lambda-1)^2 - 6))\cos(k\lambda\sigma)\big] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^3 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^5\sigma^3} \big[k\sigma(6\sin(k\sigma) + (18-24\lambda
   +k^2\sigma^2(\lambda-1)^2(4\lambda-1))\sin(k\lambda\sigma)) \notag \\
   &+24\cos(k\sigma) + (6k^2\sigma^2(\lambda-1)(2\lambda-1)-\lambda
   k^4\sigma^4(\lambda-1)^3)\cos(k\lambda\sigma)\big] \\
  \int_\sigma^{\lambda \sigma} r
 \left( \frac{r}{\sigma}-1\right)^4 \sin (kr) \mathrm{d}r =&
 \frac{1}{k^6\sigma^4}
 \big[(k\sigma(\lambda-1)(36-60\lambda+k^2\sigma^2(\lambda-1)^2(5\lambda-1))
   -1)\sin(k\lambda\sigma) -120\sin(k\sigma) \notag \\ 
   &+k\sigma(24\cos(k\sigma) -
   (24(5\lambda-4)-4k^2\sigma^2(\lambda-1)^2 (5\lambda-2) +
   \lambda k^4\sigma^4(\lambda-1)^4)\cos(k\lambda\sigma) \big]
\end{align}
\end{widetext}
\subsubsection{Averaged pair distribution  $g_\sigma(\rr)$}
